Containers and R---the Rockerverse and beyond

### 2019-12-18 manuscript.Rmd
add missing label and link for Fedora

- Alpine images
- [Images used by R-Hub](https://github.com/r-hub/rhub-linux-builders) (overlap with CI?)
- https://github.com/jlisic/R-docker-centos

@@

## Interfaces for Docker in R

>>>>

- Alpine images
- [Images used by R-Hub](https://github.com/r-hub/rhub-linux-builders) (overlap with CI?)
- https://github.com/jlisic/R-docker-centos
- Fedora > easy to install: https://github.com/ismailsunni/dockeRs

@@

## Interfaces for Docker in R
\label{interfaces}
